---
title: "Untitled"
author: "Ronald Palencia"
date: '2022-11-08'
output:
  beamer_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(quantmod)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r}
sp500 = getSymbols('^GSPC', from = '1995-1-1', auto.assign = F)
```


```{r}
tail(sp500)
```


```{r cars, echo = TRUE}
summary(cars)
```



```{python}
import pandas as pd
### permite obtener data frames directamente de internet
!pip install yfinance

```


```{python}
import yfinance as yf
```


```{python}
#define the ticker symbol
tickerSymbol = '^GSPC'

#get data on this ticker
tickerData = yf.Ticker(tickerSymbol)

#get the historical prices for this ticker
gs = tickerData.history(period='1d', start='1995-1-1', end='2022-11-7')

#see your data
gs.head(10)
```